Model for Porous Silicon Structures with a Lateral Gradient

### 2020-10-30 paper.tex
Revise to the end

We measured the reflectance spectra  at the positions indicated in
Fig. \ref{fig:SI3} on our three samples $G_1$, $G_2$,
and $G_3$, prepared using the same procedure
(Sec. \ref{sec:fabrication-ps-grin}) but applying different currents
$I_1=5\,\text{mA}$, $I_2=10\,\text{mA}$, and $I_3=20\,\text{mA}$, . The results are shown in
Figs. \ref{fig:R5}, \ref{fig:R10}, and \ref{fig:R20}.
We fitted the reflectance measurements using Eqs. \eqref{Eq:ECMR} and
\eqref{Eq:Brugg} using the local porosity $p$, and the thickness of the
film  $d$ as
adjustable parameters. We also fitted a scaling parameter $s$ to allow
for calibration variations among spectra. From the thickness we
obtained the etching rate $v=d/t$ at each position. Notice that the fits are reasonably
good. The contrast of the reflectance in the experiment is somewhat smaller
than in our fitted curves. We believe this is due to the finite width
\notaL{beams width=?} \notaC{beams width width (0.7mm) and length (2.0mm)}
of the illuminating beam of our
spectrometer. Thus, as our GRIN sample is not macroscopically homogeneous and its
properties have a gradient, the
experimental results have contributions from regions with slightly
different porosities and thicknesses, averaging out the interference
maxima and minima. We expect microscopic inhomogeneities such as
interface roughness might also reduce the contrast through scattering
and its corresponding apparent dissipation \cite{missoni2020rough}
\notaL{citar a:
  Missoni, Leandro L., Guillermo P. Ortiz, María Luz Martínez Ricci,
  Victor J. Toranzos, and W. Luis Mochán. 2020. “Rough 1D Photonic
  Crystals: A Transfer Matrix Approach.” Optical Materials 109
  (November): 110012. https://doi.org/10.1016/j.optmat.2020.110012.
}.
The loss of contrast is most notable for the thicker regions
towards the left side of Fig. \ref{fig:SI3} and for smaller
wavelengths.

@@

From the data in Table \ref{t:jpdv} we can plot the fitted porosity as
a function of the calculated density current, as shown for our three
samples in Fig. \ref{fig:p}.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{pvsj}
  \caption{Porosity as a function of current density for three samples
    $G_1$, $G_2$, $G_3$. The data points for each sample are joined by
    thick lines. The arrows point to data that correspond to
    position $x'_1=0.2\,\text{cm}$, joined to the other data by thin
    lines (see text). We include linear fits to the data from
    sample $G_3$ (thick straight line) and to that from all the
    samples (thin straight line). }
  \label{fig:p}
\end{figure}
Notice that for each sample the data points lie around straight lines,
except for one outlier point in each corresponding to position
$x'_1$. As discussed in Sec. \ref{sec:ps-grin-single}, those points
were very close to a wall of the electrolytic cell, so they were
affected by leakage currents towards the underside of the wall.
For this reason, we exclude those points from the following
analysis. We made a linear fit to the data from sample $G_3$ and to
the data from the three samples. A comparison shows that a fit to the
data of just one sample, $G_3$, turns out to be a reasonable predictor for the
porosity of all the samples.  From that fit we obtain that for our
preparation conditions
\begin{equation}\label{eq:p}
  p\approx 0.013\frac{\text{cm}^2}{\text{mA}} j_\perp+0.53.
\end{equation}

Similarly, we can plot the fitted etching rate as
a function of the calculated density current, as shown for our three
samples in Fig. \ref{fig:v}.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{vvsj}
  \caption{Etching rate as a function of current density for three samples
    $G_1$, $G_2$, $G_3$. The data points for each sample are joined by
    thick lines. The arrows point to data that correspond to
    position $x'_1=0.2\,\text{cm}$, joined to the other data by thin
    lines (see text). We include linear fits to the data from
    sample $G_3$ (thick straight line) and to that from all the
    samples (thin straight line). }
  \label{fig:v}
\end{figure}
As for the porosity, there are outlier points corresponding to the
immediate proximity of the wall of the cell, but the remaining points
lie on straight lines for each sample, and they
may all be approximated by a linear fit to the data of just one
sample, $G_3$, from which we get
\begin{equation}\label{eq:v}
  v\approx 0.35\frac{\text{cm}^2}{\text{mA}}
  \frac{\text{nm}}{\text{s}}j_\perp + 0.092\frac{\text{nm}}{{s}}.
\end{equation}

@@

The theoretical reflectance coudl as well be calculated using
\eqref{Eq:ECMR}-\eqref{eq:v} for more complicated structures, in which the
current $I$ is modulated in time, allowing the design and analysis of
non-trivial multilayered GRIN PS structures.

\section{Conclusions}
\label{sec:conclusions}
By choosing a simple geometry for our electrochemical cell, namely, a
rectangular prism, and employing a point-like electrode, we were able
to derive an expression for the calculation of the electric current
density along the surface of a Si sample. The expression was obtained
by using image charge theory and a planewise summation of Coulomb
potentials in 2D reciprocal space, and it is made up of
a rapidly converging sum of analytical terms, just a few of which
should be kept. This allows the characterization
of the porosity of a PS layer and the etching
rate for different values of the etching current density by making
optical measurements on several positions of just a
few samples. We illustrated the procedure with three samples on each of which we
measured reflectance spectra at eight different positions.
Through a optimization procedure we fitted the porosity and etching
rate corresponding to each current density.
We showed that an analysis of the data of just one of the samples, which we chose
as that with the largest current density range, yielded calibration
curves that allow the approximate prediction of the properties of the other
samples. The calibration curves can be used to design and calculate the optical
properties of other systems prepared under similar conditions, such as
multilayered GRIN systems from which photonic crystals, microcavities
and sensors with position dependent properties. This is the subject of
ongoing work. As the etching rate for the formation of porous silicon
and the resulting porosity are very sensitive to the growth conditions
and to the properties of the substrate, such as its doping,
there are no universal calibration curves. Thus, it is useful to have
a procedure that from just one sample can produce calibration curves
that may be employed for other samples grown in the same conditions.

\notaV{By choosing a simple geometry for our electrochemical cell, namely, a
rectangular prism, and employing a point-like electrode, we were able
to derive a simple expression for the calculation of the electric current
density along the surface of a Si sample. The expression was obtained
by using image charge theory and a plane-wise summation of Coulomb
potentials in reciprocal space, and it is made up of
a rapidly converging sum of analytical terms. This allowed us to
characterize the porosity of a PS layer and the etching
rate for different values of the etching current density by making
optical experiments on just a
few samples. We illustrated the procedure with two samples each of which we
measured at three different positions. These calibration curves are
very useful as the etching rate for the formation of porous silicon
and the resulting porosity is very sensitive to the growth conditions
and to the properties of the substrate, such as its doping. Thus,
there are no universal calibration curves. Having obtained these calibration curves
and being able to compute the current density at different positions
allows the prediction of the properties of GRIN structures. We
illustrated this by desigining a PS GRIN microcavity tuned at one
position to a given wavelength. (Q. for Dr. Mochan : Do we intend
to illustrate the design?) We found a good agreement between its
measured reflectance spectra at different points with the spectra
calculated from the values of the expected local current
density using the calibration curves. We also found good agreement
between the measured and the expected geometry of the system. These
results show that the use of a simple electrolytic cell and our
computational procedure does allow the accurate prediction of the
optical properties of GRIN structures, and thus we believe it will
prove helpful for the design fabrication and characterization of novel}

\section*{Acknowledgments}
\label{sec:acknowledgments}
WLM acknowledges the support of DGAPA-UNAM under grant
IN111119. \notaL{Cristian debe agradecer a conacyt y faltan
  agradecimientos de Vivechna (quizás incluyendo al icf)}
\nocite{*}
\notaL{Manda toda la bibliografía a un archivo .bib}
\notaL{Cuando esté listo, quiero que me expliques por qué incluiste
  cada uno de los artículos citados}
% \bibliography{bibligrin} %Bibliographie
%\printbibliography
%\bibliographystyle{plain}
%\bibliography{bibligrin.bib}
%\medskip
%

\bibliographystyle{unsrt}
%
\bibliography{bibligrin} %Aquí ponen el nombre del archivo .bib

\end{document}

>>>>

We measured the reflectance spectra  at the positions indicated in
Fig. \ref{fig:SI3} on our three samples $G_1$, $G_2$,
and $G_3$, prepared using the same procedure
(Sec. \ref{sec:fabrication-ps-grin}) but applying different currents
$I_1=5\,\text{mA}$, $I_2=10\,\text{mA}$, and $I_3=20\,\text{mA}$. The results are shown in
Figs. \ref{fig:R5}, \ref{fig:R10}, and \ref{fig:R20}.
We fitted the reflectance measurements using Eqs. \eqref{Eq:ECMR} and
\eqref{Eq:Brugg} using the local porosity $p$, and the thickness of the
film  $d$ as
adjustable parameters. We also fitted a scaling parameter $s$ to allow
for calibration variations among spectra. From the thickness we
obtained the etching rate $v=d/t$ at each position. Notice that the fits are reasonably
good. The contrast of the reflectance in the experiment is somewhat smaller
than in our fitted curves. We believe this is due to the finite width
$0.7\text{mm}\times2.0\text{mm}$ of the illuminating beam of our
spectrometer. Thus, as our GRIN sample is not macroscopically homogeneous and its
properties have a gradient, the
experimental results have contributions from regions with slightly
different porosities and thicknesses, averaging out the interference
maxima and minima. We expect microscopic inhomogeneities such as
interface roughness might also reduce the contrast through scattering
and its corresponding apparent dissipation \cite{missoni2020rough}.
The loss of contrast is most notable for the thicker regions
towards the left side of Fig. \ref{fig:SI3} and for smaller
wavelengths.

@@

From the data in Table \ref{t:jpdv} we can plot the fitted porosity as
a function of the calculated density current, as shown for our three
samples in Fig. \ref{fig:p}.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{pvsj}
  \caption{Porosity as a function of current density for three samples
    $G_1$, $G_2$, $G_3$. The data points for each sample are joined by
    thick lines. The arrows point to data that correspond to
    position $x'_1=0.2\,\text{cm}$, joined to the other data by thin
    lines (see text). We include linear fits to the data from
    sample $G_3$ (thick straight line) and to that from all the
    samples (thin straight line). }
  \label{fig:p}
\end{figure}
Notice that for each sample the data points lie around straight lines,
except for one outlier point in each corresponding to position
$x'_1$. As discussed in Sec. \ref{sec:ps-grin-single}, those points
were very close to a wall of the electrolytic cell, so they were
affected by leakage currents towards the underside of the wall.
For this reason, we exclude those points from the following
analysis. We made a linear fit to the data from sample $G_3$ and to
the data from the three samples. A comparison shows that a fit to the
data of just one sample, $G_3$, turns out to be a reasonable predictor for the
porosity of all the samples.  From that fit we obtain that for our
preparation conditions
\begin{equation}\label{eq:p}
  p\approx 0.013\frac{\text{cm}^2}{\text{mA}} j_\perp+0.53.
\end{equation}
The discrepancies may be due to the ill definition of the edge of the
sample (the position of the sealing o-ring) with respect to which we
measured the position of the illuminating spot. A rigid displacement along
$x$ yields mostly a horizontal shift of the results shown in
Fig. \ref{fig:p} and that can bring them into closer agreement.

Similarly, we can plot the fitted etching rate as
a function of the calculated density current, as shown for our three
samples in Fig. \ref{fig:v}.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{vvsj}
  \caption{Etching rate as a function of current density for three samples
    $G_1$, $G_2$, $G_3$. The data points for each sample are joined by
    thick lines. The arrows point to data that correspond to
    position $x'_1=0.2\,\text{cm}$, joined to the other data by thin
    lines (see text). We include linear fits to the data from
    sample $G_3$ (thick straight line) and to that from all the
    samples (thin straight line). }
  \label{fig:v}
\end{figure}
As for the porosity, there are outlier points corresponding to the
immediate proximity of the wall of the cell, but the remaining points
lie on straight lines for each sample, and they
may all be approximated by a linear fit to the data of just one
sample, $G_3$, from which we get
\begin{equation}\label{eq:v}
  v\approx 0.35\frac{\text{cm}^2}{\text{mA}}
  \frac{\text{nm}}{\text{s}}j_\perp + 0.092\frac{\text{nm}}{{s}}.
\end{equation}
The discrepancies, as in Fig. \ref{fig:p} might be due to our poor
definition of our reference position and may be eliminated by
introducing a rigid displacement along $x$ between the samples. For
multilayered samples, produced by modulating the current $I$ in time,
without changing wafers, these error source would be absent.

@@

The theoretical reflectance could as well be calculated using
\eqref{Eq:ECMR}-\eqref{eq:v} for more complicated structures, in which the
current $I$ is modulated in time, allowing the design and analysis of
non-trivial multilayered GRIN PS structures.

\section{Conclusions}
\label{sec:conclusions}
By choosing a simple geometry for our electrochemical cell, namely, a
rectangular prism, and employing a point-like electrode, we were able
to derive an expression for the calculation of the electric current
density along the surface of a Si sample. The expression was obtained
by using image charge theory and a planewise summation of Coulomb
potentials in 2D reciprocal space, and it is made up of
a rapidly converging sum of analytical terms, just a few of which
should be kept. This allows the characterization
of the porosity of a PS layer and the etching
rate for different values of the etching current density by making
optical measurements on several positions of just a
few samples. We illustrated the procedure with three samples on each of which we
measured reflectance spectra at eight different positions.
Through a optimization procedure we fitted the porosity and etching
rate corresponding to each current density.
We showed that an analysis of the data of just one of the samples, which we chose
as that with the largest current density range, yielded calibration
curves that allow the approximate prediction of the properties of the other
samples. We believe that the discrepancies we found between samples
are due to difficulties in defining a common reference position and
may be eliminated through a rigid shift along the $x$ direction.
The calibration curves can be used to design and calculate the optical
properties of other systems prepared under similar conditions, such as
multilayered GRIN systems from which photonic crystals, microcavities
and sensors with position dependent properties. This is the subject of
ongoing work. As the etching rate for the formation of porous silicon
and the resulting porosity are very sensitive to the growth conditions
and to the properties of the substrate, such as its doping,
there are no universal calibration curves. Thus, it is useful to have
a procedure that from just one sample can produce calibration curves
that may be employed for other samples grown in the same conditions.

\section*{Acknowledgments}
\label{sec:acknowledgments}
WLM acknowledges the support of DGAPA-UNAM under grant
IN111119. \notaL{Cristian debe agradecer a conacyt y faltan
  agradecimientos de Vivechna (quizás incluyendo al icf)}
\bibliographystyle{unsrt}
\bibliography{bibligrin} %Aquí ponen el nombre del archivo .bib
\end{document}
